---
title: "Introduction to StatComp20079"
author: "Yueping Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20079}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20079__ is a simple R package developed to To record the functions that need to be written during the research process and the existing methods in the papers to achieve reading (implemented through the R package _StatComp20079_) for the 'Statistical Computing' course. Two functions are considered, namely, _Lagrange_ (to approximate an unknown function) and _FCM_ (Fuzzy cluster analysis of data).


## Lagrange interpolation

The source R code for _Lagrange_ is as follows:
```{r,eval=FALSE}
Lagrange<-function(x,X,Y){
  #x为缺失值y对应的x值
  #Y为已知的所有y值组成的向量
  #X为Y向量对应的x值向量
  n<-length(X) #节点的个数
  lagr<-0 #插值多项式的初始值
  if(length(X)!=length(Y))
    stop("input error,the length of input values X and Y should be equal")
  if(n<2)
    stop("the length of X and Y should be bigger than 1")
  for(i in 1:n)
  {
    li<-1
    for(j in 1:n)
    {
      if(i!=j)
        li<-li*(x-X[j])/(X[i]-X[j])
    }
    lagr<-li*Y[i]+lagr
  }
  return(lagr)
}
```

## FCM(Fuzzy clustering algorithm)

The source R code for _FCM_ is as follows:

```{r,eval=FALSE}
FCM <- function(dat, k){
  m <- 2
  iter.max <- 1000
  eps <- 1e-06
  dat <- as.matrix(dat)
  set.seed(6386)
  v0 <- dat[sample(nrow(dat), k),] #初始聚类中心
  
  n <- nrow(dat)
  d <- matrix(0, n, k)#初始距离矩阵
  for (j in 1:k) {
    d[, j] = sqrt(rowSums(sweep(dat, 2, v0[j, ], "-")^2))#J.i,欧几里得距离
  }
  
  u <- matrix(NA, n, k)#初始隶属矩阵
  for (j in 1:k){
    for (i in 1:n){
      if (any(d[i,] == 0)){
        u[i, ] <- rep(1/k, k)
      }else{
        u[i, j] <- 1/(sum((d[i, j]/d[i, ])^(2/(m - 1))))
      }
    }
  }
  v <- t(u^m) %*% dat/colSums(u^m)
  J <- sum(d^2 * (u^m)) #目标函数
  
  iter <- 0
  j.best <- Inf
  while((iter < iter.max) && (abs(j - j.best) > eps)){
    j.best <- J
    for (j in 1:k) {
      d[, j] = sqrt(rowSums(sweep(dat, 2, v[j, ], "-")^2))
    }
    
    for (j in 1:k){
      for (i in 1:n){
        if (any(d[i,] == 0)){
          u[i, ] <- rep(1/k, k)
        }else{
          u[i, j] <- 1/(sum((d[i, j]/d[i, ])^(2/(m - 1))))#更新隶属矩阵
        }
      }
    }
    v <- t(u^m) %*% dat/colSums(u^m)
    J <- sum(d^2 * (u^m))
    iter = iter + 1
  }
  cluster_id <-  apply(u, 1, which.max)
  result <- list()
  result$u <- u
  result$v <- v
  result$cluster_id <- cluster_id
  return(result)
}
```

In order to verify the effect of the _Lagrange_ , input two vectors and observe the approximated function curve . The R code for _Lagrange_ is as follows.

```{r,eval=TRUE}
library(StatComp20079)

X <- c(-2.15,-1.00,0.01,1.02,2.03,3.25)
Y <- c(17.03,7.24,1.05,2.03,17.06,23.05)
f <- function(x)
  Lagrange(x,X,Y)
curve(f(x),-2.15,3.25)
```

The above results show that after knowing certain points of the function, the function curve can be fitted by Lagrangian interpolation.   



Take the data set iris as an example to show the clustering effect of _FCM_,The source R code is as follows:


```{r,eval=FALSE}
library(StatComp20079)
data(iris)
dat <- iris[,2:4]
result <- FCM(dat,3)
plot(iris$Sepal.Width,iris$Petal.Width,col=result$cluster_id,main="模糊聚类结果可视化",pch=19)

```

From the above figure, the data set can be clearly divided into 3 categories.

